Indexed Containers

### 2011-05-09 journal/paper.tex

\section{Indexed Functors}

@@

\section{Indexed containers}

@@

\section{Initial Algebras of Indexed Containers}

@@

\section{Terminal Co-Algebras of Indexed Containers}

@@

\section{W is still enough}

\subsection*{\ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}}

@@

\subsection*{\ensuremath{\Conid{M}} from \ensuremath{\Conid{W}}}
Since we have shown that both \ensuremath{\Conid{WI}} and \ensuremath{\Conid{MI}} types can be reduced to their 
non-indexed counterparts, it only remains to show that \ensuremath{\Conid{M}} types can be, reduced
to \ensuremath{\Conid{W}} types. This is a result from our previous work on containers~\cite{alti:cont-tcs}, though in the setting of 
indexed \ensuremath{\Conid{WI}} types, we can give a better intuition.

>>>>

\section{Indexed Functors}
\label{sec:ifunc}

@@

\section{Indexed containers}
\label{sec:icont}

@@

\section{Initial Algebras of Indexed Containers}
\label{sec:initalg}

@@

\section{Terminal Co-Algebras of Indexed Containers}
\label{sec:termcoalg}

@@

\section{W is still enough}
\label{sec:w-enough}

\subsection*{\ensuremath{\Conid{WI}} from \ensuremath{\Conid{W}}}
\label{wifromw}

@@

\subsection*{\ensuremath{\Conid{M}} from \ensuremath{\Conid{W}}}
\label{sec:mfromw}

Since we have shown that both \ensuremath{\Conid{WI}} and \ensuremath{\Conid{MI}} types can be reduced to their 
non-indexed counterparts, it only remains to show that \ensuremath{\Conid{M}} types can be, reduced
to \ensuremath{\Conid{W}} types. This is a result from our previous work on containers~\cite{alti:cont-tcs}, though in the setting of 
indexed \ensuremath{\Conid{WI}} types, we can give a better intuition.
